Twists of supersymmetric gauge theories

### 2019-09-11 paper.tex
Merging changes

\subsection{Dimension 8}
The 8-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^8$.  It has BRST fields given by a ghost, an 8d gauge field $A$, a pair of $\gg$-valued scalar fields $\phi_1$ and $\phi_2$, and a Dirac spinor field $\lambda = (\lambda_+, \lambda_-) \in S_+ \oplus S_-$.

@@

The holomorphic supercharge is stabilized by the group $\SU(4)$, and the topological supercharge is stabilized by $\spin(7)$.  If we want to stabilize the full one-parameter family describing the degeneration, we have to decompose our fields according to the action of the intersection $\SU(4) \cap \spin(7) \iso \SU(3)$.  The BRST fields decompose as
\begin{align*}
A &\mapsto A_{0,1} + A_{1,0} + \chi^0_1 + \chi^0_2 \in (\Omega^{0,1}(\CC^3) \oplus \Omega^{1,0}(\CC^3) \oplus \Omega^0(\CC^3)^2) \otimes \Omega^0(\RR^2_{x^7,x^8}) \otimes \gg\\
\lambda_+ &\mapsto \psi^+_{0,1} + \psi^+_{1,0} + \chi^+_1 + \chi^+_2 \in (\Omega^{0,1}(\CC^3) \oplus \Omega^{1,0}(\CC^3) \oplus \Omega^0(\CC^3)^2) \otimes \Omega^0(\RR^2_{x^7,x^8}) \otimes \gg\\
\lambda_- &\mapsto \psi^-_{0,1} + \psi^-_{1,0} + \chi^-_1 + \chi^-_2 \in (\Omega^{0,1}(\CC^3) \oplus \Omega^{1,0}(\CC^3) \oplus \Omega^0(\CC^3)^2) \otimes \Omega^0(\RR^2_{x^7,x^8}) \otimes \gg
\end{align*}
along with the ghost $c$ and the two scalar fields $\phi_1$ and $\phi_2$, which remain unchanged.  In terms of these component fields we can write the action of our 1-parameter family of supercharges, which we'll denote by $Q_{\mr{hol}} + tQ'$.  We choose the two supercharge $Q_{\mr{hol}}$ and $Q'$ to each be pure individually, but to have impure sum.  The action of such a supercharge can be written in terms of a quadratic and a cubic interaction as
\begin{align*}
I^{(1)}_t &= \int \langle A_{1,0}^\vee, \psi_{1,0}^- + t\psi_{1,0}^+\rangle + \langle \phi_1^\vee, \chi_1^+ + t\chi_1^- \rangle + \langle \phi_2^\vee, \chi_2^- + t\chi_2^+ \rangle + \langle (\chi_1^-)\vee + t(\chi_1^+)^\vee, \Lambda F_{1,1} \rangle + \\
&\quad + \langle (\psi^-_{1,0})^\vee + t(\psi^+_{1,0})^\vee, F_{0,2} \rangle + \langle (\psi^-_{0,1})^\vee + t(\psi^+_{0,1})^\vee, \ol \dd_{A_{0,1}} (\phi_1 + \chi_1^0) \rangle \\
I^{(2)}_t &= \int \langle (\chi_1^+)^\vee + t(\chi_1^-)^\vee, (\chi_1^+)^\vee \rangle.
\end{align*}
\chris{This is a bit of a mess, but it's a first pass guess, and I think it's correct for $t=0$.  I want to identify $F_{0,2}$ on a CY3 with a $(1,0)$ form.}

@@

\chris{There might be a clever trick to avoid these action functional calculations, involving the 10d calculation we already did to argue that certain fields definitely don't contribute (the ones that died in the 10d holomorphic twist, so we're left with only $A_{0,1}, \chi^0_1, \phi_1, \psi^+_{0,1}, \psi^+_{1,0}, \psi^-_{1,0}$ and $\chi^-_1$.) -- I need to think about it.}

>>>>

\subsection{Dimension 8}
The 8-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^8$.  It has BRST fields given by a ghost, an 8d gauge field $A$, a pair of $\gg$-valued scalar fields $\phi_1$ and $\wt \phi_1$, and a Dirac spinor field $\lambda = (\lambda_+, \lambda_-) \in S_+ \oplus S_-$.

@@

The holomorphic supercharge is stabilized by the group $\SU(4)$, and the topological supercharge is stabilized by $\spin(7)$.  If we want to stabilize the full one-parameter family describing the degeneration, we have to decompose our fields according to the action of the intersection $\SU(4) \cap \spin(7) \iso \SU(3)$.  The BRST fields decompose as
\begin{align*}
A &\mapsto A_{0,1} + A_{1,0} + \phi_2 + \wt \phi_2 \in (\Omega^{0,1}(\CC^3) \oplus \Omega^{1,0}(\CC^3) \oplus \Omega^0(\CC^3)^2) \otimes \Omega^0(\RR^2_{x^7,x^8}) \otimes \gg\\
\lambda_+ &\mapsto \psi^+_{0,1} + \psi^+_{1,0} + \chi^+ + \wt \chi^+ \in (\Omega^{0,1}(\CC^3) \oplus \Omega^{1,0}(\CC^3) \oplus \Omega^0(\CC^3)^2) \otimes \Omega^0(\RR^2_{x^7,x^8}) \otimes \gg\\
\lambda_- &\mapsto \psi^-_{0,1} + \psi^-_{1,0} + \chi^- + \wt \chi^- \in (\Omega^{0,1}(\CC^3) \oplus \Omega^{1,0}(\CC^3) \oplus \Omega^0(\CC^3)^2) \otimes \Omega^0(\RR^2_{x^7,x^8}) \otimes \gg
\end{align*}
along with the ghost $c$ and the two scalar fields $\phi_1$ and $\wt \phi_1$, which remain unchanged.  In terms of these component fields we can write the action of our 1-parameter family of supercharges, which we'll denote by $Q_{\mr{hol}} + tQ'$.  We choose the two supercharge $Q_{\mr{hol}}$ and $Q'$ to each be pure individually, but to have impure sum.  The action of such a supercharge can be written in terms of a quadratic and a cubic interaction as
\begin{align*}
I^{(1)}_t &= \int \langle A_{1,0}^\vee, \psi_{1,0}^- + t\psi_{1,0}^+\rangle + \langle \phi_1^\vee, \chi^+ + t\chi^- \rangle + \langle \phi_2^\vee, \wt \chi^- + t\wt \chi^+ \rangle + \langle (\chi^-)\vee + t(\chi^+)^\vee, \Lambda F_{1,1} \rangle + \\
&\quad + \langle (\psi^-_{1,0})^\vee + t(\psi^+_{1,0})^\vee, F_{0,2} \rangle + \langle (\psi^-_{0,1})^\vee + t(\psi^+_{0,1})^\vee, \ol \dd_{A_{0,1}} (\phi_1 + \phi_2) \rangle \\
I^{(2)}_t &= \int \langle (\chi^+)^\vee + t(\chi^-)^\vee, (\chi^+)^\vee \rangle.
\end{align*}
\chris{This is a bit of a mess, but it's a first pass guess, and I think it's correct for $t=0$.  I want to identify $F_{0,2}$ on a CY3 with a $(1,0)$ form.}

@@

\chris{There might be a clever trick to avoid these action functional calculations, involving the 10d calculation we already did to argue that certain fields definitely don't contribute (the ones that died in the 10d holomorphic twist, so we're left with only $c, A_{0,1}, \phi_1, \phi_2 \psi^+_{0,1}, \psi^+_{1,0}, \psi^-_{0,1}$ and $\chi^-$, and their antifields.) -- I need to think about it.}
